\LARGE \bf Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainity

### 2014-07-07 paper.tex
some changes to exposition, flow into prior work

\author{Michael Laskey*,Zoe McCarthy*, Sachin Patil, Pieter Abbeel and Ken Goldberg}% <-this % stops a space

@@

\vspace{10pt}
\noindent{\textbf{Grasp Quality Metrics}}: A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
We use the wrench-space Ferrari-Canny force closure quality measures \cite{ferrari1992}, which aims to maximize the disturbance that can be resisted given bounds on the contact forces.
We also consider the general case where there is friction at the contact points.
We follow the analysis of Schulman et al. \cite{schulman2011} in the discussion below.\\

@@

We use the following notation $Q(g)$ refers to the exact $L^1$ grasp quality.
It is denoted by the following

\begin{align}
Q(g) &= \mbox{max}(0,q(g)) = -d(0,\mbox{Conv}(0 \cup S(g))\\
-d(0,S) &= min_{||z|| = 1} h_{S(z)}\\
h_{S(z)} &= \mbox{sup}_{s\in S}<s,z>\\
\end{align}

We denote the Ferrari-Canny version, which approximates the friction cone by a linearized set of wrenches\cite{ferrari1992}, as $Q^-_l(g)$.\\

@@

\begin{theorem}
\label{lemma35}
For $w \in \mathbb{R}^3$, we have, for $n \in \mathbb{S}^2$ and for friction coefficient $\mu > 0$,

\begin{align}
\mbox{sup}_{x \in C(n)} <x,w> = <n,w> + \mu||n \times w||
\end{align}

@@

\begin{align}
h_{W_i(g)}(a,b) = <n_i,a+b\times(c_i-z)>+\mu ||n_i \times (a+b\times(c_i-z))||
\end{align}

@@

\begin{theorem}
We have \\

\begin{align}
q(g) = \min_{u\in \mathbb{R}^6, ||u|| =1} h_{S(g)}(u) = \min_{u\in \mathbb{R}^6, ||u|| =1} \max_{i=1,...,m} h_{W_i(g)}(u),\\
\end{align}

where $h_{S(g)}$ is convex on $\mathbb{R}^6$.
Observe that q is invariant under fixed translation of the grasp center and contact positions.
Furthermore, let $\mathbb{B}(r) = \lbrace x \in \mathbb{R}^3 : ||x|| \leq r \rbrace$.
Then q is Lipschitz continuous on grasps with $m$ contact points lying in the set $X = \lbrace (c_1, \dots, c_m,n_1, \dots,n_m,z) : (c_i-z) \in \mathbb{B}(r), n_i \in \mathbb{S}^2 \rbrace$ with a Lipschitz constant given by $L= (1+\mu)(1+r)$ and where the chose distance measure

@@

Since $Q(g) = max(0,q(g))$, Q is also Lipschitz continuous with the same constant L on X. 
\end{theorem}

>>>>

\author{Michael Laskey*, Zoe McCarthy*, Sachin Patil, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space

@@

\vspace{10pt}
\noindent{\textbf{Grasp Quality Metrics}}: A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
We use the wrench-space Ferrari-Canny force closure quality measures \cite{ferrari1992}, which aims to maximize the disturbance that can be resisted given bounds on the contact forces.
We also consider the general case where there is friction at the contact points.
\\

@@

We follow the notation of \cite{pokorny2013classical} and we re-state some of their central theorems for our use here.
For more detail, refer there.
$Q(g)$ refers to the exact $L^1$ grasp quality.
It is denoted by the following

\begin{align}
  Q(g) &= \mbox{max}(0,q(g)) = -d(0,\mbox{Conv}(\{0\} \cup S(g))\\
-d(0,S) &= min_{||z|| = 1} h_{S(z)}\\
h_{S(z)} &= \mbox{sup}_{s\in S}\langle s,z\rangle\\
\end{align}

We denote the Ferrari-Canny version, which approximates the friction cone by a linearized set of wrenches\cite{ferrari1992}, as $Q^-_l(g)$.
The next theorem shows that the linearized wrench set used in Ferrari-Canny calculates a lower bound on $Q(g)$.\\

@@

\begin{theorem}
\label{lemma35}
  \cite{pokorny2013classical}
For $w \in \mathbb{R}^3$, we have, for $n \in \mathbb{S}^2$ and for friction coefficient $\mu > 0$,

\begin{align}
\mbox{sup}_{x \in C(n)} \langle x,w \rangle = \langle n,w \rangle + \mu||n \times w||
\end{align}

@@

\[
h_{W_i(g)}(a,b) =
 \langle n_i,a+b\times(c_i-z)\rangle +
\]
\begin{align}
 +\mu ||n_i \times (a+b\times(c_i-z))||
\end{align}

@@

\begin{theorem}
  \cite{pokorny2013classical}
We have \\

\begin{align}
q(g) 
=
\min_{u\in \mathbb{R}^6, ||u|| =1} h_{S(g)}(u) 
=
\end{align}
\[
\min_{u\in \mathbb{R}^6, ||u|| =1} \max_{i=1,...,m} h_{W_i(g)}(u),
\]

where $h_{S(g)}$ is convex on $\mathbb{R}^6$.
$q$ is invariant under fixed translation of the grasp center and contact positions.
Furthermore, let $\mathbb{B}(r) = \lbrace x \in \mathbb{R}^3 : ||x|| \leq r \rbrace$.
Then $q$ is Lipschitz continuous on grasps with $m$ contact points lying in the set $X = \lbrace (c_1, \dots, c_m,n_1, \dots,n_m,z) : (c_i-z) \in \mathbb{B}(r), n_i \in \mathbb{S}^2 \rbrace$ with a Lipschitz constant given by $L= (1+\mu)(1+r)$ and where we use distance measure

@@

Since $Q(g) = max(0,q(g))$, $Q$ is also Lipschitz continuous with the same constant $L$ on $X$. 
\end{theorem}
